Supplementary Materials

### 2020-05-29 analysis/analysis.Rmd
Fixed fill issue with subgroup comparison plots

```{r setup, include=FALSE}

library(bookdown)
library(tidyverse)
library(brms)
library(tidybayes)
library(ggridges)
library(latex2exp)
library(see)
library(ggthemes)
library(patchwork)
library(magick)

@@

# read in some helper functions that will be used later
source("scripts/helper_functions.R")
```

@@

```{r define_comparison_summary_function}
comparison_summary <- function(subgroup_comp_dat, greater, measurement_lab) {
  # compute probabilties
  subgroup_comp_dat %>%
    group_by(key, index, normal) %>%
    summarise(
      mean_value = mean(value),
      prob_one_tailed = if_else(greater == TRUE, mean(value > 0), mean(value < 0)))  %>%
    mutate(
      measurement = measurement_lab,
      index_labs = as.numeric(as.factor(index)),
      lab_cols = v_cols[index_labs],
      prob_cat = cut(prob_one_tailed, c(0, 0.5, 0.75, 0.9, 0.99, 1))) -> comp_summary_dat

>>>>

```{r setup, include=FALSE}
library(bookdown)
library(tidyverse)
library(brms)
library(tidybayes)
library(ggridges)
library(latex2exp)
library(see)
library(ggthemes)
library(patchwork)
library(magick)

@@

# read in some helper functions that will be used later
source("scripts/helper_functions.R")

options(mc.cores = parallel::detectCores())
```

@@

```{r define_comparison_summary_function}
comparison_summary <- function(subgroup_comp_dat, greater, measurement_lab) {
  # compute probabilties
  subgroup_comp_dat %>%
    group_by(key, index, normal) %>%
    summarise(
      mean_value = mean(value),
      prob_one_tailed = if_else(greater == TRUE, mean(value > 0), mean(value < 0)))  %>%
    mutate(
      prob_one_tailed = if_else(prob_one_tailed==0, 0.01, prob_one_tailed),
      measurement = measurement_lab,
      index_labs = as.numeric(as.factor(index)),
      lab_cols = v_cols[index_labs],
      prob_cat = cut(prob_one_tailed, c(0, 0.5, 0.75, 0.9, 0.99, 1))) -> comp_summary_dat
